Program Transformations for miniKanren

### 2020-07-04 papers/aplas/text/evaluation.tex

\begin{align*}
  &type \ term = \\
  &| \ BConst \ of \ Bool \\
  &| \ IConst \ of \ Int \\
  &| \ Var \ of \ Int \\
  &| \ term + term \\
  &| \ term * term \\
  &| \ term = term \\
  &| \ term < term \\
  &| \ \underline{let} \ term \ \underline{in} \ term \\
  &| \ \underline{if} \ term \ \underline{then} \ term \ \underline{else} \ term
\end{align*}

>>>>

%% \begin{align*}
%%   &type \ term = \\
%%   &| \ BConst \ of \ Bool \\
%%   &| \ IConst \ of \ Int \\
%%   &| \ Var \ of \ Int \\
%%   &| \ term + term \\
%%   &| \ term * term \\
%%   &| \ term = term \\
%%   &| \ term < term \\
%%   &| \ \underline{let} \ term \ \underline{in} \ term \\
%%   &| \ \underline{if} \ term \ \underline{then} \ term \ \underline{else} \ term
%% \end{align*}

\[\begin{array}{lllll}
  type \ term = &\ BConst \ of \ Bool &| \ IConst \ of \ Int &| \ Var \ of \ Int & \\
  & | \ term + term &| \ term * term &| \ term = term &| \ term < term \\
  &| \ \underline{let} \ term \ \underline{in} \ term 
  &\multicolumn{2}{l}{| \ \underline{if} \ term \ \underline{then} \ term \ \underline{else} \ term} &
\end{array}\]
